FoRTE baseline

### 2019-04-23 analysis/paper/paper.Rmd
Add meta-analysis result figure

```{r methods_captions}
param_dist_cap <- paste(
  "Input parameter distributions."
)
```

@@

- Summary:
    - LAI time series with uncertainties, faceted by model structure
- Structural uncertainty details
    - Understory light environment and how it affects species matters
    - The multiple-scatter
        - Fig: RTM comparison (Radiation profile)
        - Fig: Crown model comparison
        - Fig: Trait plasticity?
- Uncertainty analysis
    - Which parameters contribute the most uncertainty?
    - Structural vs. parameteric uncertainty

>>>>

```{r methods_captions}
param_dist_cap <- paste(
  "Input parameter distributions from PEcAn trait meta-analysis."
)
```

@@

- Summary:
    - Time series of aggregate variables (GPP, NPP, AGB, Total LAI), with error bars by structure
- Structural uncertainty details
    - Understory light environment and how it affects species matters
    - The multiple-scatter
        - Fig: RTM comparison (Radiation profile)
        - Fig: Crown model comparison
        - Fig: Trait plasticity?
- Uncertainty analysis
    - Which parameters contribute the most uncertainty?
    - Structural vs. parameteric uncertainty
